cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Updated Table 3

```{r}
arg_branching_tb <- tibble(arg = c("n",
                          "p",
                          "k"), 
                        exp = c("A numeric value representing the number of points.",
                                "A numeric value representing the number of dimensions.",
                                "A numeric value representing the number of clusters."))
```

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Explanation"), table.pos = "H") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

```{r}
arg_branching_tb <- tibble(arg = c("n",
                          "k"), 
                          type = c("integer", "integer"),
                        exp = c("Number of points.",
                                "Number of clusters."))
```

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), table.pos = "H") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

@@

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "3cm") |>
  column_spec(2, width = "9cm")
```
